A new model to predict survival in patients with end-stage liver disease

### 2022-07-19 analysis/article.Rmd
fix: labm requires vs.

```{r tbl-observed-vs-expected-mortality, results = "asis", echo = FALSE, message = FALSE}
tbl_observed_vs_expected_mortality$ObservedMortality <-
    tbl_observed_vs_expected_mortality$ObservedMortality * 100
tbl_observed_vs_expected_mortality$ExpectedMortality <-
    tbl_observed_vs_expected_mortality$ExpectedMortality * 100
knitr::kable(
    cbind(
        row.names(tbl_observed_vs_expected_mortality),
        tbl_observed_vs_expected_mortality
    ),
    row.names = FALSE,
    col.names =
        c(
            "MELD category",
            "Observed deaths (n)",
            "Expected deaths (n)",
            "Standardized mortality ratio (SMR)",
            "Observed mortality (%)",
            "Expected mortality (%)"
        ),
    caption = paste0(
        "Observed vs MELD-expected 90-day mortality. ",
        "MELD mortality values are taken from @wiesner2003. ",
        "All patients censored before day 90 are ignored for ",
        " the calculation of the MELD-expected deaths. ",
        "SMR, Standardized mortality ratio = observed deaths/expected deaths."
    ),
    digits = 1
)
```

>>>>

```{r tbl-observed-vs-expected-mortality, results = "asis", echo = FALSE, message = FALSE}
tbl_observed_vs_expected_mortality$ObservedMortality <-
    tbl_observed_vs_expected_mortality$ObservedMortality * 100
tbl_observed_vs_expected_mortality$ExpectedMortality <-
    tbl_observed_vs_expected_mortality$ExpectedMortality * 100
knitr::kable(
    cbind(
        row.names(tbl_observed_vs_expected_mortality),
        tbl_observed_vs_expected_mortality
    ),
    row.names = FALSE,
    col.names =
        c(
            "MELD category",
            "Observed deaths (n)",
            "Expected deaths (n)",
            "Standardized mortality ratio (SMR)",
            "Observed mortality (%)",
            "Expected mortality (%)"
        ),
    caption = paste0(
        "Observed vs. MELD-expected 90-day mortality. ",
        "MELD mortality values are taken from @wiesner2003. ",
        "All patients censored before day 90 are ignored for ",
        " the calculation of the MELD-expected deaths. ",
        "SMR, Standardized mortality ratio = observed deaths/expected deaths."
    ),
    digits = 1
)
```
